---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MyFirstPackage

The goal of MyFirstPackage is to accompany the talk by Dietz & Knudson at the Boston University BSA seminar held on December 18, 2020.

## Installation

You can install the development version of MyFirstPackage from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("knudson1/WiADS2020", build_vignettes = TRUE)
```

## Talk Slides

After installing, you can access the slides using the following code:
``` r
library(MyFirstPackage)
vignette("WiADS_Slides")
```
You can also get there directly using the link: https://github.com/knudson1/WiADS2020/blob/boston/doc/WiADS_Slides.pdf

## Example

This is an example of the two functions included in this package:

```{r example}
library(MyFirstPackage)

#Calculate effective sample size
minESS(p = 2, alpha = 0.05, epsilon = 0.05)

#Calculate target PSRF using 5 chains
target_psrf(m = 5, p = 2, alpha = 0.05, epsilon = 0.05)

```
